---
title: "Stigma Analysis"
author: "Alexandrea Tucker"
date: "4/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r, include = FALSE}
# this line for setting the working directory
# set to the directory that holds the data
# setwd("C:/Users/tucam/Documents/DS 401/stigma data")
```


## Libraries  

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(corpus)
library(stringr)
library(ggthemes)
library(tidytext)
library(textdata)
```

## Functions  

```{r}
Clean_String <- function(string){
  # Lowercase
  temp <- tolower(string)
  # Remove everything that is not a number or letter (may want to keep more 
  # stuff in your actual analyses). 
  temp <- stringr::str_replace_all(temp,"[^a-zA-Z\\s]", " ")
  # Shrink down to just one white space
  temp <- stringr::str_replace_all(temp,"[\\s]+", " ")
  # Split it
  temp <- stringr::str_split(temp, " ")[[1]]
  # Get rid of trailing "" if necessary
  indexes <- which(temp == "")
  if(length(indexes) > 0){
    temp <- temp[-indexes]
  } 
  return(paste(temp, collapse = ' '))
}
```


## Data


### Addictionary data

Dictionary of addiction words (words associated w/ stigma are indicated)

```{r}
addictionary <- read.csv("addictionary.csv")
```


### Comments data

Comments (data collected by Harsha)

```{r}
comments <- read.csv("retoplevelcomments.csv")
```

#### Clean comments data



There issues when exporting the data from excel. Due to limited time, I do not have time to fix this problem. Here is a quick fix. I only want subreddits correctly named

```{r}
subnames <- c('alcohol', 'alcoholicsanonymous', 'alcoholism', 'stopdrinking', 'dryalcoholics', 'REDDITORSINRECOVERY', 'Alcoholism_Medication', 'addiction', 'Sober', 'meth', 'Drugs', 'leaves', 'cocaine', 'cripplingalcoholism')

correctcomments <- filter(comments, subreddit %in% subnames)
```

### Posts data

Posts (data collected by Harsha)

```{r}
posts <- read.csv("redditposts.csv")
```


#### Clean posts data


There issues when exporting the data from excel. Due to limited time, I do not have time to fix this problem. Here is a quick fix. I only want subreddits correctly named

```{r}
subnames <- c('alcohol', 'alcoholicsanonymous', 'alcoholism', 'stopdrinking', 'dryalcoholics', 'REDDITORSINRECOVERY', 'Alcoholism_Medication', 'addiction', 'Sober', 'meth', 'Drugs', 'leaves', 'cocaine', 'cripplingalcoholism')

correct <- filter(posts, subreddit %in% subnames)
```


These are the only the columns I want to consider:

```{r}
subposts <- correct %>% select(created_utc, subreddit, author, dom, url, title, selftext, id, name)
```


```{r}
subposts[, 1] <- sapply(subposts[, 1], as.numeric)
```


This takes some time to run. The final cleaned posts dataset is cleanposts1.

```{r}
#columns interested in in posts
cleanposts <- subposts %>% select(subreddit, author, dom, url, title, selftext, id, name)

cleanposts1 <- cleanposts

for (i in 1:length(cleanposts1$title)) {
  cleanposts1$title[i] <- Clean_String(cleanposts$title[i])
  cleanposts1$selftext[i] <- Clean_String(cleanposts$selftext[i])
}
```


## Stigmatizing Words

```{r}
# stigma words from addictionary
stigmadict <- addictionary %>% filter(Type == "Stigma Alert")
stigmawords <- stigmadict %>% select(Word)
```

```{r}
head(stigmawords)
```


```{r}
# stems from stigma words
stigmalist <- stigmawords$Word

tokens <- text_tokens(stigmalist, stemmer = "en")
tokenslist <- unlist(tokens)
stems <- tokenslist[-c(21,23)]
```

```{r}
head(data.frame(stems))
```



## Which post titles or selftext contain stigma?

To answer this question we will use the the stigma stems. 

```{r}

contains_stigma <- c()
for (i in 1:length(cleanposts1$title)) {
  stigma_indicator <- FALSE
  for (j in 1:length(stems)) {
    if (grepl(stems[j], cleanposts1$title[i], fixed = TRUE)) {
      stigma_indicator <- TRUE
    }
    if (grepl(stems[j], cleanposts1$selftext[i], fixed = TRUE)) {
      stigma_indicator <- TRUE
    }
  }
  
  contains_stigma <- c(contains_stigma, stigma_indicator)
  
}
```



```{r}
cleanposts1$contains_stigma <- contains_stigma


ggplot(data = cleanposts1) + geom_bar(mapping = aes(x = contains_stigma))
```


## Which comments contain stigma?

```{r}
comment_contains_stigma <- c()
for (i in 1:length(correctcomments$body)) {
  stigma_indicator <- FALSE
  for (j in 1:length(stems)) {
    if (grepl(stems[j], correctcomments$body[i], fixed = TRUE)) {
      stigma_indicator <- TRUE
    }
  }
  
  comment_contains_stigma <- c(comment_contains_stigma, stigma_indicator)
  
}
```

```{r}
correctcomments$contains_stigma <- comment_contains_stigma
```




Save data cause I don't want to run all of this again

```{r}
write_excel_csv(data.frame(comment_contains_stigma), "C:/Users/tucam/Documents/DS 401/stigma data/comment_contains_stigma_r.csv")


write_excel_csv(correctcomments, "C:/Users/tucam/Documents/DS 401/stigma data/correctcomments_r.csv")


write_excel_csv(cleanposts1, "C:/Users/tucam/Documents/DS 401/stigma data/cleanposts1_r.csv")
```


## Data with stigma

```{r}
stigma_posts <- read.csv("cleanposts1_r.csv")

stigma_comments <- read.csv("correctcomments_r.csv")

names(stigma_comments)[1] <- "body"
```




```{r}
ggplot(data = stigma_posts) + geom_bar(mapping = aes(x = contains_stigma)) +
  labs(x = "Contains Stigma", y = "Count") + 
  ggtitle("Count of Post Titles Containing Stigma") +
  theme(plot.title = element_text(size = 10, face = "bold", margin = margin(10, 0, 10, 0))) +
  theme_stata() + scale_colour_stata()
```

```{r}
ggplot(data = stigma_comments) + geom_bar(mapping = aes(x = contains_stigma)) +
  labs(x = "Contains Stigma", y = "Count") + 
  ggtitle("Count of Comments Containing Stigma") +
  theme(plot.title = element_text(size = 10, face = "bold", margin = margin(10, 0, 10, 0))) +
  theme_stata() + scale_colour_stata()
```




```{r}
affin <- get_sentiments("afinn")
```

## Measure Sentiment on Posts

```{r}

tidy_posts <- stigma_posts %>% mutate(linenumber = row_number()) %>% unnest_tokens(word, title)

```


### NRC dictionary 

Here, I am looking at the negative dictionary. I am counting the number of words associated with negativity. 

```{r}
nrc_negative <- get_sentiments("nrc") %>% filter(sentiment == "negative")

all <- tidy_posts %>%inner_join(nrc_negative) %>% count(word, sort = TRUE)

negative <- tidy_posts %>% filter(contains_stigma == TRUE) %>%inner_join(nrc_negative) %>% count(word, sort = TRUE)
other <- tidy_posts %>% filter(contains_stigma == FALSE) %>%inner_join(nrc_negative) %>% count(word, sort = TRUE)
```


```{r}
total_post_sentiment <- negative %>% inner_join(get_sentiments("bing")) %>% pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(sentiment = positive - negative)
```


```{r}
total_post_sentiment_other <- other %>% inner_join(get_sentiments("bing")) %>% pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(sentiment = positive - negative)
```

```{r}
total_post_sentiment_all <- tidy_posts %>% inner_join(get_sentiments("bing")) %>% 
  count(contains_stigma, index = linenumber, sentiment) %>% 
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(sentiment = positive - negative)
```


```{r}
ggplot(total_post_sentiment_all, aes(index, sentiment, fill = contains_stigma)) + geom_col(show.legend = FALSE) +
  facet_wrap(~contains_stigma)
```


## Sentiment Analysis of Comment Data

```{r}

tidy_comments <- stigma_comments %>% mutate(linenumber = row_number()) %>% unnest_tokens(word, body)

```


### NRC dictionary: measure count of negative words 


```{r}
all_comments <- tidy_comments %>% inner_join(nrc_negative) %>% count(word, sort = TRUE)
```

```{r}
total_comment_sentiment_all <- tidy_comments %>% inner_join(get_sentiments("bing")) %>% 
  count(contains_stigma, index = linenumber, sentiment) %>% 
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>%
  mutate(sentiment = positive - negative)
```

```{r}
ggplot(total_comment_sentiment_all, aes(index, sentiment, fill = contains_stigma)) + geom_col(show.legend = FALSE) +
  facet_wrap(~contains_stigma)
```




```{r}
affin_posts_stigma <- tidy_posts %>% filter(contains_stigma == TRUE) %>% inner_join(get_sentiments("afinn")) %>%
  group_by(index = linenumber) %>%
  summarise(sentiment = sum(value)) %>%
  mutate(method = "AFINN", contains_stigma = TRUE)
```

```{r}
affin_posts_nostigma <- tidy_posts %>% filter(contains_stigma == FALSE) %>% inner_join(get_sentiments("afinn")) %>%
  group_by(index = linenumber) %>%
  summarise(sentiment = sum(value)) %>%
  mutate(method = "AFINN", contains_stigma = FALSE)
```

ggplot(data = stigma_posts) + geom_bar(mapping = aes(x = contains_stigma)) +
  labs(x = "Contains Stigma", y = "Count") + 
  ggtitle("Count of Post Titles Containing Stigma") +
  theme(plot.title = element_text(size = 10, face = "bold", margin = margin(10, 0, 10, 0))) +
  theme_stata() + scale_colour_stata()
```{r}
bind_rows(affin_posts_stigma, affin_posts_nostigma) %>%
  ggplot(aes(index, sentiment, fill = contains_stigma)) + 
  labs(x = "Index", y = "Sentiment Score") +
  ggtitle("Sentiment Score of Posts") +
  geom_col(show.legend = FALSE) +
  facet_wrap(~contains_stigma, ncol = 1, scales= "free_y") +
  ylim(-6, 6) +
  theme_stata() + scale_colour_stata()
```
```{r}
mean(affin_posts_nostigma$sentiment)
```
```{r}
mean(affin_posts_stigma$sentiment)
```




```{r}
affin_comments_stigma <- tidy_comments %>% filter(contains_stigma == TRUE) %>% inner_join(get_sentiments("afinn")) %>%
  group_by(index = linenumber) %>%
  summarise(sentiment = sum(value)) %>%
  mutate(method = "AFINN", contains_stigma = TRUE)
```


```{r}
affin_comments_nostigma <- tidy_comments %>% filter(contains_stigma == FALSE) %>% inner_join(get_sentiments("afinn")) %>%
  group_by(index = linenumber) %>%
  summarise(sentiment = sum(value)) %>%
  mutate(method = "AFINN", contains_stigma = FALSE)
```
bind_rows(affin_posts_stigma, affin_posts_nostigma) %>%
  ggplot(aes(index, sentiment, fill = contains_stigma)) + 
  labs(x = "Index", y = "Sentiment Score") +
  ggtitle("Sentiment Score of Posts") +
  geom_col(show.legend = FALSE) +
  facet_wrap(~contains_stigma, ncol = 1, scales= "free_y") +
  ylim(-6, 6) +
  theme_stata() + scale_colour_stata(

```{r}


bind_rows(affin_comments_stigma, affin_comments_nostigma) %>%
  ggplot(aes(index, sentiment, fill = contains_stigma)) + 
  labs(x = "Index", y = "Sentiment Score") +
  ggtitle("Sentiment Score of Comments") +
  geom_col(show.legend = FALSE) +
  facet_wrap(~contains_stigma, ncol = 1, scales= "free_y") +
  ylim(-6, 6) +
  theme_stata() + scale_colour_stata()
```
```{r}
mean(affin_comments_nostigma$sentiment)
```
```{r}
mean(affin_comments_stigma$sentiment)
```